Astr 513: Homework 2

### 2016-03-10 HW2/HW2.tex

\section{Part D}
\label{sec:partD}
Bayes' Theorem says
\begin{equation}
  P(A|B) = \frac{P(B|A)P(A)}{P(B)}
\end{equation}
where $P(X|Y)$ is a conditional probability of $X$ given $Y$, and $P(Z)$ is 
refered to as a \textit{prior} belief on what the value of $Z$ should be.
Frequentists equate the two conditional probabilities, but this is incorrect
in the Bayesian approach precisely because you wish to be informed by the 
priors. In this part, we assume \textit{uniform} priors on our posterior
parameters $u_x$, $u_y$ and $g$, and in addition to this there is no Jacobian 
transformation. Thus we can write for the conditional probability
\begin{align}
  \label{eq:bayesian_conditional}
  P_B(u_x,u_y,g|R,h,g) = & \frac{1}{(2\pi)^{3/2}\sigma_R\sigma_h\sigma_g} \exp\left(-\frac{(2u_xu_y/g - R_0)^2}{2\sigma_R^2}\right)\times \\ &\exp\left(-\frac{(u_y^2/2g-h_0)^2}{2\sigma_h^2}\right) \exp\left(-\frac{(g-g_0)^2}{2\sigma_g^2}\right)
\end{align}
where we have written $R$ and $h$ as functions of $u_x$, $u_y$ and $g$. Just as in class,
this expression is missing the Jacobian term,
$2u_y^2/g^2$, as calculated in \autoref{sec:partC}. Thus, if we assume flat priors
\begin{equation}
  \label{eq:priors_partD}
  P_{pr}(u_x) = P_{pr}(u_y) = 1
\end{equation}
then the ratio of the two probabilities is simply this Jacobian
\begin{equation}
  \label{eq:prob_ratio}
  \frac{P_f}{P_b} = \frac{2u_y^2}{g^2}.
\end{equation}
Interestingly, this ratio is not unitless, 
but this is not an issue since in the Bayesian 
framework we neglect the normalization terms anyway, 
which carry units with them.

>>>>

\section{Part D}
\label{sec:partD}
Bayes' Theorem says
\begin{equation}
  P(A|B) = \frac{P(B|A)P(A)}{P(B)}
\end{equation}
where $P(X|Y)$ is a conditional probability of $X$ given $Y$, and $P(Z)$ is 
referred to as a \textit{prior} belief on what the value of $Z$ should be.
Frequentists equate the two conditional probabilities, but this is incorrect
in the Bayesian approach precisely because you wish to be informed by the 
priors. In this part, we assume \textit{uniform} priors on our posterior
parameters $u_x$, $u_y$ and $g$, and in addition to this there is no Jacobian 
transformation. Thus we can write for the conditional probability
\begin{align}
  \label{eq:bayesian_conditional}
  P_B(u_x,u_y,g|R,h,g) = & \frac{1}{(2\pi)^{3/2}\sigma_R\sigma_h\sigma_g} \exp\left(-\frac{(2u_xu_y/g - R_0)^2}{2\sigma_R^2}\right)\times \\ &\exp\left(-\frac{(u_y^2/2g-h_0)^2}{2\sigma_h^2}\right) \exp\left(-\frac{(g-g_0)^2}{2\sigma_g^2}\right)
\end{align}
where we have written $R$ and $h$ as functions of $u_x$, $u_y$ and $g$. Just as in class,
this expression is missing the Jacobian term,
$2u_y^2/g^2$, as calculated in \autoref{sec:partC}. Thus, if we assume flat priors
\begin{equation}
  \label{eq:priors_partD}
  P_{pr}(u_x) = P_{pr}(u_y) = 1
\end{equation}
then the ratio of the two probabilities is simply this Jacobian
\begin{equation}
  \label{eq:prob_ratio}
  \frac{P_f}{P_b} = \frac{2u_y^2}{g^2}.
\end{equation}
Interestingly, this ratio is not unitless, 
but this is not an issue since in the Bayesian 
framework we neglect the normalization terms anyway, 
which carry units with them.
